The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-09-26 paper.tex
fix a typo in a cross-reference
add a discussion of polarization leakage

\subsection{$m$-Mode Analysis Imaging}

@@

Antenna gain calibration is accomplished using alternating least squares otherwise known as
``stefcal'' \citep{2008ISTSP...2..707M, 2014A&A...571A..97S}.  \citet{2008ISTSP...2..707M} and
\citet{2014A&A...571A..97S}. The calibration routine is written in the Julia programming language
\citep{doi:10.1137/141000671}, and is publicly available
online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
any later version).

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
    \caption{
        This plot shows the local spectral index (estimated by means of a local T-T plot) as a
        contour plot. The contours are overlaid on the three-color image from
        Figure~\ref{three-color}.
    }
    \label{fig:internal-spectral-index}
\end{figure*}

@@

>>>>

\subsection{$m$-Mode Analysis Imaging}\label{sec:mmode-imaging}

@@

Antenna gain calibration is accomplished using a variant of alternating least squares colloquially
known as ``stefcal'' \citep{2008ISTSP...2..707M, 2014A&A...571A..97S}. The calibration routine is
written in the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
any later version).

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
    \caption{
        This plot shows the local spectral index (estimated by means of a local T-T plot) as a
        contour plot. The contours are overlaid on the three-color image from
        Figure~\ref{fig:three-color}.
    }
    \label{fig:internal-spectral-index}
\end{figure*}

@@

\subsection{Polarization Leakage}

\citet{2015PhRvD..91h3514S} describe how to generalize $m$-mode analysis to account for a polarized
sky observed with a polarized antenna beam. Heretofore this generalization has been neglected in the
discussion of $m$-mode analysis imaging.  At low frequencies, increasingly rapid Faraday rotation
leads to depolarization. Therefore polarization fractions are generally expected to decrease at low
frequencies (varying with ionospheric conditions). \citet{2016ApJ...830...38L} detected the presence
of diffuse polarized emission on degree angular scales with the MWA, also finding typical
depolarization ratios of $\sim0.3$ for pulsars at 154~MHz relative to 1.4~GHz, although there was a
large variance between pulsars. Even more depolarization is expected at frequencies $\le
73.152$~MHz, but crossed-dipole antennas with extremely large primary beams will naturally introduce
large polarization leakage terms at low elevations.  It is instructive to compute what impact this
will have on the unpolarized imaging process.

In order to understand the effect of polarization leakage, a point source with 10\% polarization in
Stokes-$Q$ was simulated at the location of Cas A.  The simulated visibilities were computed using
the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
every direction on the sky, this introduces a direction-dependent leakage of Stokes-$Q$ into
Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about 7 hours
every day skirting the horizon where the polarization leakage is large, so by placing the simulated
source at the location of Cas A, we are engineering a situation where the polarization leakage from
Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
PSF.
